---
title: |
       | \vspace{-2.5cm} Results of the measurement of physical behavior
output: 
   pdf_document:
     latex_engine: xelatex
params:
  assessor_title: NA
  assessor_name: NA
  assessor_surname: NA
  patient_title: NA
  patient_name: NA
  patient_surname: NA
  sex: NA
  age: NA
  weight: NA
  epoch: NA
  start_date: NA
  end_date: NA
  device: NA
  position: NA
  side: NA
  sampling_rate: NA
  filter: NA
  start_day_analysis: NA
  end_day_analysis: NA
  axis_weartime: NA
  frame_size: NA
  allowanceFrame_size: NA
  streamFrame_size: NA
  equation_mets: NA
  bmr_kcal_d: NA
  axis_sed: NA
  axis_mvpa: NA
  sed_cutpoint: NA
  mpa_cutpoint: NA
  vpa_cutpoint: NA
  minimum_wear_time_for_analysis: NA
  results_by_day: NA
  results_summary_means: NA
  results_summary_medians: NA
  mvpa_lines: NA
  sed_lines: NA
  ratio_lines: NA
  df_with_computed_metrics: NA
  graph_int_distri_bands: NA
  graph_int_distri_models: NA
  mean_breaks_sed: NA
  p_breaks_sed: NA
  p_alpha_sed: NA 
  p_MBD_sed: NA
  p_UBD_sed: NA 
  p_gini_sed: NA
  mean_breaks_pa: NA
  p_breaks_pa: NA 
  p_alpha_pa: NA
  p_MBD_pa: NA
  p_UBD_pa: NA
  p_gini_pa: NA
  rendered_by_shiny: FALSE
  geometry: "left=2cm, right=2cm, top=1cm, bottom=1cm"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo = FALSE)
library(magrittr)
library(ggplot2)
library(patchwork)

df1_means <- params$results_summary_means
df1_medians <- params$results_summary_medians
df2 <- params$results_by_day
axis_mvpa_graph <- ifelse(params$axis_mvpa == "vertical axis", "axis1", 
              ifelse(params$axis_mvpa == "vector magnitude", "vm",
                     "na"))

height_factor1 = nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.8
height_factor1 <- ifelse(height_factor1 <= 6, nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.9, height_factor1)
height_factor2 = params$results_summary_means$valid_days * 0.75
height_factor2 <- ifelse(height_factor2 <= 6, nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.9, height_factor2)
height_factor3 = nlevels(as.factor(params$df_with_computed_metrics$date)) * 1.5

options("scipen"=100, "digits"=4)
```


# Information
<hr>

**Patient:** `r params$patient_surname` `r params$patient_name`  | **Date:**  `r Sys.Date()` | **Assessor:**  `r params$assessor_surname` `r params$assessor_name`

**Age:** `r params$age` yr | **Sex:**  `r params$sex` | **Weight:** `r params$weight` kg | **Measurement period:** `r format(params$start_date, "%Y-%m-%d %H:%M:%S")` to `r format(params$end_date, "%Y-%m-%d %H:%M:%S")` | **Estimated Basal Metabolic Rate (BMR):** `r format(round(params$bmr_kcal_d, 2), nsmall = 2)` kcal/day (Estimation based on Henry equations [2005, doi: 10.1079/PHN2005801])

**Device:** `r params$device` | **Position:** `r params$position` | **Side:** `r params$side` | **Sampling rate:** `r params$sampling_rate` Hz | **Filter:** `r params$filter`

**Epoch:** `r params$epoch` s | **Nonwear time:** Based on `r params$axis_weartime`, interval of `r params$frame_size` min with zero count for nonwear time detection, interval of `r params$allowanceFrame_size` min with nonzero counts allowed during a nonwear period, interval of `r params$streamFrame_size` min with zero count around detected activity to confirm nonwear time | **MET equation:** `r params$equation_mets` | **Axis used for PA intensity categorization:** `r params$axis_mvpa` | **Cut-points:** <`r params$sed_cutpoint` counts/min for SED, $\geqslant$ `r params$mpa_cutpoint` counts/min for MPA, $\geqslant$ `r params$vpa_cutpoint` counts/min for VPA

**Period of the day considered to count wear time:** from `r params$start_day_analysis` to `r params$end_day_analysis`

**Minimum number of hours with wear time to validate a day:** `r params$minimum_wear_time_for_analysis` hours

**Abbreviations:** SED = sedentary, LPA =  light physical activity, MPA = moderate physical activity, VPA = vigorous physical activity, MVPA = moderate-to-vigorous physical activity, PAL = physical activity level


# Results
<hr>

## Activity volume  metrics

### Temporal distribution of activity intensity
```{r,  fig.height = height_factor1, fig.width=13}
plot_data_with_intensity(
  data = params$df_with_computed_metrics, 
  metric = axis_mvpa_graph,
  valid_wear_time_start = params$start_day_analysis,
  valid_wear_time_end = params$end_day_analysis
  )
if (params$rendered_by_shiny)
  shiny::setProgress(0.25)  # set progress to 25%
```

### Results by day
```{r, fig.height=10, fig.width = 17, warning=FALSE, message=FALSE}
create_fig_res_by_day(
  df2, 
  params$minimum_wear_time_for_analysis, 
  params$start_day_analysis, 
  params$end_day_analysis, 
  language = "en",
  metrics = "volume"
  ) + theme(plot.margin = margin(1, 1, 1, 1, "cm"), axis.text.x = element_text(hjust = 1.1))
```

### Means | Medians computed using valid days
```{r }
create_flextable_summary(
  results_summary_means = df1_means, 
  results_summary_medians = df1_medians, 
    language = "en",
    metrics = "volume",
    epoch_label = paste0(params$epoch, "s")
  )
if (params$rendered_by_shiny)
  shiny::setProgress(0.5)  # set progress to 50%
```

### Comparisons with norms and recommendations
```{r, fig.height=9, fig.width = 17, warning=FALSE, message=FALSE}
# PAL
g_pal <- create_fig_pal(score = df1_means[["pal"]], "en") + theme(plot.margin = margin(2, 1, 0.5, 1, "cm"))
  
# Steps
g_steps <- create_fig_steps(score = df1_means[["total_steps"]], "en") + theme(plot.margin = margin(0, 1, 0.5, 1, "cm"))

# MVPA
g_mvpa <- create_fig_mvpa(score = df1_means[["minutes_MVPA"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# SED
g_sed <- create_fig_sed(score = df1_means[["minutes_SED"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# MVPA/SED ratio
g_ratio <- create_fig_ratio_mvpa_sed(score = df1_means[["ratio_mvpa_sed"]], "en") + theme(plot.margin = margin(0, 1, 1, 1, "cm"))

# Whole figure
g_pal / g_steps / (g_mvpa | g_sed | g_ratio) + 
    plot_layout(heights = c(0.8, 0.7, 1.5)) & theme(legend.justification = "center")
```

### Comments
```{r, echo = F}
# Determining physical activity guidelines status
guidelines_status <- get_guidelines_status(df1_means[["mets_hours_mvpa"]], language = "en")

# Determining PAL status
pal_status <- get_pal_status(df1_means[["pal"]], language = "en")
```

According to the [Food and Agriculture Organization of the United Nations (FAO)](http://www.fao.org/3/y5686e/y5686e.pdf), the PAL of the patient could be characterized as **`r pal_status`**. After converting moderate and vigorous physical activity minutes to MET-hours, the estimate of the daily mean of MVPA volume for the patient is `r paste0(format(round(df1_means[["mets_hours_mvpa"]], 1), nsmall = 1))` MET-hr, which could correspond to falling **`r guidelines_status`** (i.e., 7.5-15.0 MET-hr a week, or 1.07-2.14 MET-hr a day).


## Step accumulation metrics

### Results by day
```{r, fig.height=7, fig.width = 17, warning=FALSE, message=FALSE}
create_fig_res_by_day(
  df2, 
  params$minimum_wear_time_for_analysis, 
  params$start_day_analysis, 
  params$end_day_analysis, 
  language = "en",
  metrics = "step_acc"
  ) + theme(plot.margin = margin(1, 1, 1, 1, "cm"), axis.text.x = element_text(hjust = 1.1))
```

### Means | Medians computed using valid days
```{r }
create_flextable_summary(
  df1_means, 
  df1_medians, 
    language = "en",
    metrics = "step_acc",
    epoch_label = paste0(params$epoch, "s")
  )

if (params$rendered_by_shiny)
  shiny::setProgress(0.75)  # set progress to 75%
```

## Intensity distribution metrics

### Results by day
```{r, fig.height=9, fig.width = 17, warning=FALSE, message=FALSE}
create_fig_res_by_day(
  df2, 
  params$minimum_wear_time_for_analysis, 
  params$start_day_analysis, 
  params$end_day_analysis, 
  language = "en",
  metrics = "int_distri",
  epoch_label = paste0(params$epoch, "s")
  ) + theme(plot.margin = margin(1, 1, 1, 1, "cm"), axis.text.x = element_text(hjust = 1.1))
```

### Means | Medians computed using valid days
```{r }
create_flextable_summary(
  df1_means, 
  df1_medians, 
    language = "en",
    metrics = "int_distri",
    epoch_label = paste0(params$epoch, "s")
  )
```

### Radar view based on means of valid days
```{r, fig.align = "center", out.width='50%', out.height='50%', fig.width=8, fig.height=8}
cor_factor <- 60 / params$epoch

create_fig_mx_summary(
data = df1_means,
labels = NULL,
mpa_cutpoint = params$mpa_cutpoint / cor_factor, 
vpa_cutpoint = params$vpa_cutpoint / cor_factor
)  + theme(legend.position = c(0.15, 0.08))
```

\newpage

## Sedentary behaviour accumulation metrics based on valid days

### Temporal distribution of sedentary bouts
```{r, fig.height = height_factor2, fig.width=13}
if(length(params$p_breaks_sed) == 1) {
  cat("No results. Results can be obtained using 60-s epochs only.")
} else {
  params$p_breaks_sed
}
```

### Alpha coefficient, median bout duration (MBD), usual bout duration (UBD), and Gini index
```{r, fig.height=6, fig.width=19}
if(length(params$p_breaks_sed) == 1) {
  cat("No results. Results can be obtained using 60-s epochs only.")
} else {
  
  p1 <- params$p_alpha_sed + guides(color = "none", fill = "none")
  p2 <- params$p_MBD_sed   + guides(color = "none", fill = "none")
  p3 <- params$p_UBD_sed
  p4 <- params$p_gini_sed
 
  (p1  | p2 | p3 | p4) + plot_layout(guides = "collect") & 
    theme(legend.position = 'bottom',
          axis.title = element_text(size = 15),
          legend.title = element_text(size = 17),
          legend.text = element_text(size = 15)
          )
}
```

\newpage

## Physical activity accumulation metrics based on valid days

### Temporal distribution of physical activity bouts
```{r, fig.height = height_factor2, fig.width=13}
if(length(params$p_breaks_pa) == 1) {
  cat("No results. Results can be obtained using 60-s epochs only.")
} else {
  params$p_breaks_pa
}
if (params$rendered_by_shiny)
  shiny::setProgress(1)  # set progress to 100%
```

### Alpha coefficient, median bout duration (MBD), usual bout duration (UBD), and Gini index
```{r, fig.height=6, fig.width=19}
if(length(params$p_breaks_pa) == 1) {
  cat("No results. Results can be obtained using 60-s epochs only.")
} else {
  p1 <- params$p_alpha_pa + guides(color = "none", fill = "none")
  p2 <- params$p_MBD_pa   + guides(color = "none", fill = "none")
  p3 <- params$p_UBD_pa
  p4 <- params$p_gini_pa
 
  (p1  | p2 | p3 | p4) + plot_layout(guides = "collect") & 
    theme(legend.position = 'bottom',
          axis.title = element_text(size = 15),
          legend.title = element_text(size = 17),
          legend.text = element_text(size = 15)
          )
}
```

