---
title: \vspace{-2cm} Results for the measurement of physical behavior
output: 
   pdf_document:
     latex_engine: xelatex
params:
  assessor_title: NA
  assessor_name: NA
  assessor_surname: NA
  patient_title: NA
  patient_name: NA
  patient_surname: NA
  sex: NA
  age: NA
  weight: NA
  epoch: NA
  start_date: NA
  end_date: NA
  device: NA
  position: NA
  side: NA
  sampling_rate: NA
  filter: NA
  start_day_analysis: NA
  end_day_analysis: NA
  axis_weartime: NA
  frame_size: NA
  allowanceFrame_size: NA
  streamFrame_size: NA
  equation_mets: NA
  bmr_kcal_d: NA
  axis_sed: NA
  axis_mvpa: NA
  sed_cutpoint: NA
  mpa_cutpoint: NA
  vpa_cutpoint: NA
  minimum_wear_time_for_analysis: NA
  results_by_day: NA
  results_summary_means: NA
  results_summary_medians: NA
  mvpa_lines: NA
  sed_lines: NA
  ratio_lines: NA
  rendered_by_shiny: FALSE
  geometry: "left=2cm, right=2cm, top=1cm, bottom=1cm"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo = FALSE)
library(magrittr)
library(ggplot2)
library(patchwork)

df1_means <- params$results_summary_means
df1_medians <- params$results_summary_medians
df2 <- params$results_by_day

options("scipen"=100, "digits"=4)
```

# Information

**Patient:** `r params$patient_surname` `r params$patient_name`  | **Date:**  `r Sys.Date()` | **Assessor:**  `r params$assessor_surname` `r params$assessor_name`

**Age:** `r params$age` yr | **Sex:**  `r params$sex` | **Weight:** `r params$weight` kg | **Measurement period:** `r format(params$start_date, "%Y-%m-%d %H:%M:%S")` to `r format(params$end_date, "%Y-%m-%d %H:%M:%S")` | **Estimated Basal Metabolic Rate (BMR):** `r format(round(params$bmr_kcal_d, 2), nsmall = 2)` kcal/day (Estimation based on Henry equations [2005, doi: 10.1079/PHN2005801].)

**Device:** `r params$device` | **Position:** `r params$position` | **Side:** `r params$side` | **Sampling rate:** `r params$sampling_rate` Hz | **Filter:** `r params$filter`.

**Epoch:** `r params$epoch` s | **Nonwear time:** Based on `r params$axis_weartime`, interval of `r params$frame_size` min with zero count for nonwear time detection, interval of `r params$allowanceFrame_size` min with nonzero counts allowed during a nonwear period, interval of `r params$streamFrame_size` min with zero count around detected activity to confirm nonwear time | **MET equation:** `r params$equation_mets` | **Axis used for PA intensity categorization:** `r params$axis_mvpa` | **Cut-points:** <`r params$sed_cutpoint` counts/min for SED, $\geqslant$ `r params$mpa_cutpoint` counts/min for MPA, $\geqslant$ `r params$vpa_cutpoint` counts/min for VPA.

**Period of the day considered to count wear time:** from `r params$start_day_analysis` to `r params$end_day_analysis`.

**Minimum number of hours with wear time to validate a day**: `r params$minimum_wear_time_for_analysis` hours.

**Abbreviations:** SED = sedentary, LPA =  light physical activity, MPA = moderate physical activity, VPA = vigorous physical activity, MVPA = moderate-to-vigorous physical activity, PAL = physical activity level.


# Results

```{r }
create_flextable_summary(df1_means, df1_medians, language = "en")
```


```{r, fig.height=18, fig.width = 17, warning=FALSE, message=FALSE}
# PAL
g_pal <- create_fig_pal(score = df1_means[["pal"]], "en") + theme(plot.margin = margin(2, 1, 0.5, 1, "cm"))
  
# Steps
g_steps <- create_fig_steps(score = df1_means[["total_steps"]], "en") + theme(plot.margin = margin(0, 1, 0.5, 1, "cm"))
if (df1_means[["total_steps"]] > 18000) {g_steps <- g_steps + annotate("text", label = "The score is \nbeyond the limits!", x = 0.25, y = 9000, size = 7, color = "red", fontface = "bold")}

if (params$rendered_by_shiny)
  shiny::setProgress(0.5)  # set progress to 50%

# MVPA
g_mvpa <- create_fig_mvpa(score = df1_means[["minutes_MVPA"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))
if (df1_means[["minutes_MVPA"]] > 100) {g_mvpa <- g_mvpa + annotate("text", label = "The score is \nbeyond the limits!", x = 50, y = 0.5, size = 7, color = "red", fontface = "bold")}

# SED
g_sed <- create_fig_sed(score = df1_means[["minutes_SED"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))
if (df1_means[["minutes_SED"]] > 15*60) {g_sed <- g_sed + annotate("text", label = "The score is \nbeyond the limits!", x = 7.5, y = 2, size = 7, color = "red", fontface = "bold")}

# MVPA/SED ratio
g_ratio <- create_fig_ratio_mvpa_sed(score = df1_means[["ratio_mvpa_sed"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))
if (df1_means[["ratio_mvpa_sed"]] > 0.4) {g_ratio <- g_ratio + annotate("text", label = "The score is \nbeyond the limits!", x = 0.2, y = 0.8, size = 7, color = "red", fontface = "bold")}

# Daily results
g_all_days <- create_fig_res_by_day(
  df2, 
  params$minimum_wear_time_for_analysis, 
  params$start_day_analysis, 
  params$end_day_analysis, 
  language = "en"
  ) + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# Whole figure
g_pal / g_steps / (g_mvpa | g_sed | g_ratio) /  g_all_days + 
    plot_layout(heights = c(0.8, 0.7, 1.5, 4)) & theme(legend.justification = "center")
```


# Comments

```{r, echo = F}
# Determining physical activity guidelines status
guidelines_status <- get_guidelines_status(df1_means[["mets_hours_mvpa"]], language = "en")

# Determining PAL status
pal_status <- get_pal_status(df1_means[["pal"]], language = "en")

# Ratio MVPA / SED comment
comment_ratio <- get_ratio_mvpa_sed_comment(df1_means[["ratio_mvpa_sed"]], language = "en")

if (params$rendered_by_shiny)
  shiny::setProgress(1)  # set progress to 100%
```

According to the [Food and Agriculture Organization of the United Nations (FAO)](http://www.fao.org/3/y5686e/y5686e.pdf), the PAL of the patient could be characterized as **`r pal_status`**. After converting moderate and vigorous physical activity minutes to MET-hours, the estimate of the daily mean of MVPA volume for the patient is `r paste0(format(round(df1_means[["mets_hours_mvpa"]], 1), nsmall = 1))` MET-hr, which could correspond to falling **`r guidelines_status`** (i.e., 7.5-15.0 MET-hr a week, or 1.07-2.14 MET-hr a day). Based on the MVPA/SED ratio, **`r paste(comment_ratio)`**.


