---
title: D-PPAC results
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    df_print: paged
toc-title: "Summary"
params:
  assessor_title: NA
  assessor_name: NA
  assessor_surname: NA
  patient_title: NA
  patient_name: NA
  patient_surname: NA
  sex: NA
  age: NA
  weight: NA
  epoch: NA
  start_date: NA
  end_date: NA
  device: NA
  position: NA
  side: NA
  sampling_rate: NA
  filter: NA
  start_day_analysis: NA
  end_day_analysis: NA
  axis_weartime: NA
  frame_size: NA
  allowanceFrame_size: NA
  streamFrame_size: NA
  equation_mets: NA
  bmr_kcal_d: NA
  axis_sed: NA
  axis_mvpa: NA
  sed_cutpoint: NA
  mpa_cutpoint: NA
  vpa_cutpoint: NA
  minimum_wear_time_for_analysis: NA
  results_by_day: NA
  results_summary_means: NA
  results_summary_medians: NA
  dppac_table: NA
  dppac_diff_raw: NA
  dppac_amount_raw: NA
  dppac_total_raw: NA
  dppac_diff_rasch: NA
  dppac_amount_rasch: NA
  dppac_total_rasch: NA 
  rendered_by_shiny: FALSE
  geometry: "left=2cm, right=2cm, top=1cm, bottom=1cm"

---

```{css, echo=FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo = FALSE)
library(magrittr)
library(ggplot2)
library(patchwork)

options("scipen"=100, "digits"=4)
```

# Information

**Patient:** `r params$patient_surname` `r params$patient_name`  | **Date:**  `r Sys.Date()` | **Assessor:**  `r params$assessor_surname` `r params$assessor_name`

**Age:** `r params$age` yr | **Sex:**  `r params$sex` | **Weight:** `r params$weight` kg | **Measurement period:** `r format(params$start_date, "%Y-%m-%d %H:%M:%S")` to `r format(params$end_date, "%Y-%m-%d %H:%M:%S")`

**Device:** `r params$device` | **Position:** `r params$position` | **Side:** `r params$side` | **Sampling rate:** `r params$sampling_rate` Hz | **Filter:** `r params$filter`

**Epoch:** `r params$epoch` s | **Nonwear time:** Based on `r params$axis_weartime`, interval of `r params$frame_size` min with zero count for nonwear time detection, interval of `r params$allowanceFrame_size` min with nonzero counts allowed during a nonwear period, interval of `r params$streamFrame_size` min with zero count around detected activity to confirm nonwear time

**Period of the day considered to count wear time:** from `r params$start_day_analysis` to `r params$end_day_analysis`

**Minimum number of hours with wear time to validate a day:** `r params$minimum_wear_time_for_analysis` hours


# Summary
```{r, fig.width=12}

diff_raw <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_diff_raw), aes(x, y, label = paste0(label, " / 20"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Difficulty score (raw)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#00CEF1", color = "white", size = 10)
  )

amount_raw <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_amount_raw), aes(x, y, label = paste0(label, " / 17"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Amount score (raw)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#39cccc", color = "white", size = 10)
  )

total_raw <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_total_raw), aes(x, y, label = paste0(label, " / 37"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Total score (raw)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#605ca8", color = "white", size = 10)
  )

if (params$rendered_by_shiny)
  shiny::setProgress(0.5)  # set progress to 50%

diff_rasch <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_diff_rasch), aes(x, y, label = paste0(label, " / 100"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Difficulty score (Rasch)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#00CEF1", color = "white", size = 10)
  )

amount_rasch <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_amount_rasch), aes(x, y, label = paste0(label, " / 100"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Amount score (Rasch)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#39cccc", color = "white", size = 10)
  )

total_rasch <-
  ggplot(data = data.frame(x = 0.1, y = 0.6, label = params$dppac_total_rasch), aes(x, y, label = paste0(label, " / 100"))) +
  geom_text(size = 17, color = "white", fontface = "bold", hjust = 0) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1), expand = FALSE) +
  annotate("text", x = 0.1, y = 0.2, label = "Total score (Rasch)", color = "white", fontface = "bold", hjust = 0, size = 6) +
  theme_void() +
  theme(
    panel.background = element_rect(fill = "#605ca8", color = "white", size = 10)
  )
  
(diff_raw | amount_raw | total_raw) / (diff_rasch | amount_rasch | total_rasch)

if (params$rendered_by_shiny)
  shiny::setProgress(1)  # set progress to 100%
```

\pagebreak 

# Details
```{r}
flextable::set_flextable_defaults(fonts_ignore = TRUE)
flextable::flextable(params$dppac_table) %>%
   flextable::theme_zebra() %>%
   flextable::align(align = "left", part = "all" ) %>%
   flextable::width(j = "Day", width = 1) %>%
   flextable::width(j = "Item", width = 3.2) %>%
   flextable::width(j = c("Difficulty score", "Amount score"), width = 2.2) %>%
   flextable::align(j = "Difficulty score", align = "center", part = "body") %>%
   flextable::align(j = "Amount score", align = "center", part = "body") %>%
   flextable::align(j = "Difficulty score", align = "center", part = "header") %>%
   flextable::align(j = "Amount score", align = "center", part = "header")
```




