---
title: Results of the measurement of physical behavior
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    df_print: paged
toc-title: "Summary"
params:
  assessor_title: NA
  assessor_name: NA
  assessor_surname: NA
  patient_title: NA
  patient_name: NA
  patient_surname: NA
  sex: NA
  age: NA
  weight: NA
  epoch: NA
  start_date: NA
  end_date: NA
  device: NA
  position: NA
  side: NA
  sampling_rate: NA
  filter: NA
  start_day_analysis: NA
  end_day_analysis: NA
  axis_weartime: NA
  frame_size: NA
  allowanceFrame_size: NA
  streamFrame_size: NA
  equation_mets: NA
  bmr_kcal_d: NA
  axis_sed: NA
  axis_mvpa: NA
  sed_cutpoint: NA
  mpa_cutpoint: NA
  vpa_cutpoint: NA
  minimum_wear_time_for_analysis: NA
  results_by_day: NA
  results_summary_means: NA
  results_summary_medians: NA
  mvpa_lines: NA
  sed_lines: NA
  ratio_lines: NA
  df_with_computed_metrics: NA
  mean_breaks_sed: NA
  p_breaks_sed: NA
  p_alpha_sed: NA 
  p_MBD_sed: NA
  p_UBD_sed: NA 
  p_gini_sed: NA
  mean_breaks_pa: NA
  p_breaks_pa: NA 
  p_alpha_pa: NA
  p_MBD_pa: NA
  p_UBD_pa: NA
  p_gini_pa: NA
  rendered_by_shiny: FALSE
  geometry: "left=2cm, right=2cm, top=1cm, bottom=1cm"

---

```{css, echo=FALSE}
.title {
  font-weight: bold;
}

h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 23px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo = FALSE)
library(magrittr)
library(ggplot2)
library(patchwork)

df1_means <- params$results_summary_means
df1_medians <- params$results_summary_medians
df2 <- params$results_by_day
axis_mvpa_graph <- ifelse(params$axis_mvpa == "vertical axis", "axis1", 
              ifelse(params$axis_mvpa == "vector magnitude", "vm",
                     "na"))

height_factor1 = nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.75
height_factor1 <- ifelse(height_factor1 <= 6, nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.9, height_factor1)
height_factor2 = params$results_summary_means$valid_days * 0.75
height_factor2 <- ifelse(height_factor2 <= 6, nlevels(as.factor(params$df_with_computed_metrics$date)) * 0.9, height_factor2)

options("scipen"=100, "digits"=4)
```


# Information
<hr>

**Patient:** `r params$patient_surname` `r params$patient_name`  | **Date:**  `r Sys.Date()` | **Assessor:**  `r params$assessor_surname` `r params$assessor_name`

**Age:** `r params$age` yr | **Sex:**  `r params$sex` | **Weight:** `r params$weight` kg | **Measurement period:** `r format(params$start_date, "%Y-%m-%d %H:%M:%S")` to `r format(params$end_date, "%Y-%m-%d %H:%M:%S")` | **Estimated Basal Metabolic Rate (BMR):** `r format(round(params$bmr_kcal_d, 2), nsmall = 2)` kcal/day (Estimation based on Henry equations [2005, doi: 10.1079/PHN2005801])

**Device:** `r params$device` | **Position:** `r params$position` | **Side:** `r params$side` | **Sampling rate:** `r params$sampling_rate` Hz | **Filter:** `r params$filter`

**Epoch:** `r params$epoch` s | **Nonwear time:** Based on `r params$axis_weartime`, interval of `r params$frame_size` min with zero count for nonwear time detection, interval of `r params$allowanceFrame_size` min with nonzero counts allowed during a nonwear period, interval of `r params$streamFrame_size` min with zero count around detected activity to confirm nonwear time | **MET equation:** `r params$equation_mets` | **Axis used for PA intensity categorization:** `r params$axis_mvpa` | **Cut-points:** <`r params$sed_cutpoint` counts/min for SED, $\geqslant$ `r params$mpa_cutpoint` counts/min for MPA, $\geqslant$ `r params$vpa_cutpoint` counts/min for VPA

**Period of the day considered to count wear time:** from `r params$start_day_analysis` to `r params$end_day_analysis`

**Minimum number of hours with wear time to validate a day:** `r params$minimum_wear_time_for_analysis` hours

**Abbreviations:** SED = sedentary, LPA =  light physical activity, MPA = moderate physical activity, VPA = vigorous physical activity, MVPA = moderate-to-vigorous physical activity, PAL = physical activity level


# Results
<hr>

## Activity volume metrics
### Temporal distribution of activity intensity
```{r, out.width='100%',  fig.height = height_factor1}
plot_data_with_intensity(
  data = params$df_with_computed_metrics, 
  metric = axis_mvpa_graph,
  valid_wear_time_start = params$start_day_analysis,
  valid_wear_time_end = params$end_day_analysis
  )
```

### Results by day
```{r}
reactable::reactable(params$results_by_day %>%
                       dplyr::rename(
                        Date = date,
                        "Wear time" = wear_time,
                        "Total counts Axis 1" = total_counts_axis1,
                        "Total counts VM" = total_counts_vm,
                        "Axis 1 per min" = axis1_per_min,
                        "VM per min" = vm_per_min,
                        "Total steps" = total_steps,
                        "Total kcal" = total_kcal,
                        "Minutes SED" = minutes_SED,
                        "Minutes LPA" = minutes_LPA,
                        "Minutes MPA" = minutes_MPA,
                        "Minutes VPA" = minutes_VPA,
                        "Minutes MVPA" = minutes_MVPA,
                        "% wear time SED" = percent_SED,
                        "% wear time LPA" = percent_LPA,
                        "% wear time MPA" = percent_MPA,
                        "% wear time VPA" = percent_VPA,
                        "% wear time MVPA" = percent_MVPA,
                        "Max steps 60 min" = max_steps_60min,
                        "Max steps 30 min" = max_steps_30min,
                        "Max steps 20 min" = max_steps_20min,
                        "Max steps 5 min" = max_steps_5min,
                        "Max steps 1 min" = max_steps_1min,
                        "Peak steps 60 min" = peak_steps_60min,
                        "Peak steps 30 min" = peak_steps_30min,
                        "Peak steps 20 min" = peak_steps_20min,
                        "Peak steps 5 min" = peak_steps_5min,
                        "Peak steps 1 min" = peak_steps_1min,
                        "MVPA MET-hr" = mets_hours_mvpa,
                        "MVPA/SED ratio" = ratio_mvpa_sed,
                        "PAL" = pal
                       ),  
                striped = TRUE,
                list(
                     "Date" = reactable::colDef(
                       style = list(position = "sticky", left = 0, background = "#CCCCCC", zIndex = 1),
                       headerStyle = list(position = "sticky", left = 0,  background = "#fff", zIndex = 1)
                     ),
                     "Wear time"          = reactable::colDef(minWidth = 160),
                     "Total counts Axis 1" = reactable::colDef(minWidth = 160),
                     "Total counts VM"     = reactable::colDef(minWidth = 160),
                     "Axis 1 per min"      = reactable::colDef(minWidth = 160),
                     "VM per min"          = reactable::colDef(minWidth = 160),
                     "Total steps"          = reactable::colDef(minWidth = 160),
                     "Total kcal"          = reactable::colDef(minWidth = 160),
                     "Minutes SED"         = reactable::colDef(minWidth = 160),
                     "Minutes LPA"         = reactable::colDef(minWidth = 160),
                     "Minutes MPA"         = reactable::colDef(minWidth = 160),
                     "Minutes VPA"         = reactable::colDef(minWidth = 160),
                     "Minutes MVPA"        = reactable::colDef(minWidth = 160),
                     "% wear time SED"     = reactable::colDef(minWidth = 160),
                     "% wear time LPA"     = reactable::colDef(minWidth = 160),
                     "% wear time MPA"     = reactable::colDef(minWidth = 160),
                     "% wear time VPA"     = reactable::colDef(minWidth = 160),
                     "% wear time MVPA"    = reactable::colDef(minWidth = 160),
                     "Max steps 60 min"    = reactable::colDef(minWidth = 160),
                     "Max steps 30 min"    = reactable::colDef(minWidth = 160),
                     "Max steps 20 min"    = reactable::colDef(minWidth = 160),
                     "Max steps 5 min"     = reactable::colDef(minWidth = 160),
                     "Max steps 1 min"     = reactable::colDef(minWidth = 160),
                     "Peak steps 60 min"   = reactable::colDef(minWidth = 160),
                     "Peak steps 30 min"   = reactable::colDef(minWidth = 160),
                     "Peak steps 20 min"   = reactable::colDef(minWidth = 160),
                     "Peak steps 5 min"    = reactable::colDef(minWidth = 160),
                     "Peak steps 1 min"    = reactable::colDef(minWidth = 160),
                     "MVPA MET-hr"         = reactable::colDef(minWidth = 160),
                     "MVPA/SED ratio"      = reactable::colDef(minWidth = 160),
                     "PAL"                 = reactable::colDef(minWidth = 160)
                     )
                )
```

### Results summarized over valid days (main metrics)
```{r, out.width='100%'}
reactable::reactable(
  tibble::tibble(
          Metric = c("Number of valid days",
                     "Wear time",
                     "Total kilocalories",
                     "Physical activity level (PAL)",
                     "Total number of steps",
                     "SED time",
                     "LPA time",
                     "MVPA time",
                     "SED wear time proportion",     
                     "LPA wear time proportion",     
                     "MVPA wear time proportion",    
                     "MVPA dose",                        
                     "MVPA/SED ratio"
          ),
          
          "Daily mean | median over valid days" = c(
            paste0(df1_means[["valid_days"]], " day(s)"),
            
            paste0(format(round(df1_means[["wear_time"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_means[["wear_time"]]), ") | ",
                   format(round(df1_medians[["wear_time"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_medians[["wear_time"]]), ")"),  
            
            paste0(format(round(df1_means[["total_kcal"]], 2), nsmall = 2),   " kcal | ", format(round(df1_medians[["total_kcal"]], 2), nsmall = 2), " kcal"),
            
            paste0(format(round(df1_means[["pal"]], 2), nsmall = 2),  " | ", format(round(df1_medians[["pal"]], 2), nsmall = 2)),  
            
            paste0(round(df1_means[["total_steps"]], 0), " steps | ", round(df1_medians[["total_steps"]], 0), " steps"), 
            
            paste0(format(round(df1_means[["minutes_SED"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_means[["minutes_SED"]]), ") | ",  
                   format(round(df1_medians[["minutes_SED"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_medians[["minutes_SED"]]), ")"),  
            
            paste0(format(round(df1_means[["minutes_LPA"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_means[["minutes_LPA"]]), ") | ",  
                   format(round(df1_medians[["minutes_LPA"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_medians[["minutes_LPA"]]), ")"), 
            
            paste0(format(round(df1_means[["minutes_MVPA"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_means[["minutes_MVPA"]]), ") | ",
                   format(round(df1_medians[["minutes_MVPA"]], 1), nsmall = 1), " min (", hms::hms(minutes = df1_medians[["minutes_MVPA"]]), ")"),  
            
            paste0(format(round(df1_means[["percent_SED"]], 1), nsmall = 1), " % | ", format(round(df1_medians[["percent_SED"]], 1), nsmall = 1), " %"),
            
            paste0(format(round(df1_means[["percent_LPA"]], 1), nsmall = 1), " % | ", format(round(df1_medians[["percent_LPA"]], 1), nsmall = 1), " %"),      
            
            paste0(format(round(df1_means[["percent_MVPA"]], 1), nsmall = 1), " % | ", format(round(df1_medians[["percent_MVPA"]], 1), nsmall = 1), " %"),                 
            
            paste0(format(round(df1_means[["mets_hours_mvpa"]], 2), nsmall = 2), " MET-hr | ", format(round(df1_medians[["mets_hours_mvpa"]], 2), nsmall = 2), " MET-hr"),         
            
            paste0(format(round(df1_means[["ratio_mvpa_sed"]], 2), nsmall = 2), " | ", format(round(df1_medians[["ratio_mvpa_sed"]], 2), nsmall = 2)))
        ),   striped = TRUE, defaultPageSize = 15
)

if (params$rendered_by_shiny)
  shiny::setProgress(0.5)  # set progress to 50%
```

### Graphical summary
```{r, fig.height=18, fig.width = 17, warning=FALSE, message=FALSE}
# PAL
g_pal <- create_fig_pal(score = df1_means[["pal"]], "en") + theme(plot.margin = margin(2, 1, 0.5, 1, "cm"))
  
# Steps
g_steps <- create_fig_steps(score = df1_means[["total_steps"]], "en") + theme(plot.margin = margin(0, 1, 0.5, 1, "cm"))

# MVPA
g_mvpa <- create_fig_mvpa(score = df1_means[["minutes_MVPA"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# SED
g_sed <- create_fig_sed(score = df1_means[["minutes_SED"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# MVPA/SED ratio
g_ratio <- create_fig_ratio_mvpa_sed(score = df1_means[["ratio_mvpa_sed"]], "en") + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# Daily results
g_all_days <- create_fig_res_by_day(
  df2, 
  params$minimum_wear_time_for_analysis, 
  params$start_day_analysis, 
  params$end_day_analysis, 
  language = "en"
  ) + theme(plot.margin = margin(0, 1, 0, 1, "cm"))

# Whole figure
g_pal / g_steps / (g_mvpa | g_sed | g_ratio) /  g_all_days + 
    plot_layout(heights = c(0.8, 0.7, 1.5, 4)) & theme(legend.justification = "center")
```


### Comments

```{r, echo = F}
# Determining physical activity guidelines status
guidelines_status <- get_guidelines_status(df1_means[["mets_hours_mvpa"]], language = "en")

# Determining PAL status
pal_status <- get_pal_status(df1_means[["pal"]], language = "en")
```

According to the [Food and Agriculture Organization of the United Nations (FAO)](http://www.fao.org/3/y5686e/y5686e.pdf), the PAL of the patient could be characterized as **`r pal_status`**. After converting moderate and vigorous physical activity minutes to MET-hours, the estimate of the daily mean of MVPA volume for the patient is `r paste0(format(round(df1_means[["mets_hours_mvpa"]], 1), nsmall = 1))` MET-hr, which could correspond to falling **`r guidelines_status`** (i.e., 7.5-15.0 MET-hr a week, or 1.07-2.14 MET-hr a day).

## Sedentary behaviour accumulation metrics based on valid days
### Temporal distribution of sedentary bouts
```{r, out.width='100%', fig.height = height_factor2}
if(length(params$p_breaks_sed) == 1) {
  cat("No result. Results can be obtained using 60-s epochs only.")
} else {
  params$p_breaks_sed
}
```

### Alpha coefficient, median bout duration (MBD), usual bout duration (UBD), and Gini index
```{r, out.width='100%', out.height='60%', fig.height=11, fig.width=11}
if(length(params$p_breaks_sed) == 1) {
  cat("No result. Results can be obtained using 60-s epochs only.")
} else {
  ((params$p_alpha_sed + theme(legend.position = "none")) | (params$p_MBD_sed + theme(legend.position = "none"))) / (params$p_UBD_sed | params$p_gini_sed) + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
}
```

## Physical activity accumulation metrics based on valid days
### Temporal distribution of physical activity bouts
```{r, out.width='100%', fig.height = height_factor2}
if(length(params$p_breaks_pa) == 1) {
  cat("No result. Results can be obtained using 60-s epochs only.")
} else {
  params$p_breaks_pa
}
if (params$rendered_by_shiny)
  shiny::setProgress(1)  # set progress to 100%
```

### Alpha coefficient, median bout duration (MBD), usual bout duration (UBD), and Gini index
```{r, out.width='100%', out.height='60%', fig.height=11, fig.width=11}
if(length(params$p_breaks_pa) == 1) {
  cat("No result. Results can be obtained using 60-s epochs only.")
} else {
  ((params$p_alpha_pa + theme(legend.position = "none")) | (params$p_MBD_pa + + theme(legend.position = "none"))) / (params$p_UBD_pa | params$p_gini_pa) + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
}
```
