---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

# activAnalyzer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/pydemull/activAnalyzer/branch/master/graph/badge.svg)](https://codecov.io/gh/pydemull/activAnalyzer?branch=master)
[![R-CMD-check](https://github.com/pydemull/activAnalyzer/workflows/R-CMD-check/badge.svg)](https://github.com/pydemull/activAnalyzer/actions)
<!-- badges: end -->

activAnalyzer is a shinny app that was developed to analyze daily physical behavior data recorded at the hip in adults using an ActiGraph accelerometer (.agd files). Once analysis is completed, the app allows to export results (summarized by day and averaged over valid days) to .csv files and to generate a report of the measurement (.pdf file). All the configured inputs relevant for interpreting the results are recorded in the report. Be sure that the inputs that are configured when generating the report correspond to the analysis that was actually performed (in other words, avoid modifying the inputs after generating satisfactory results). Please read the [user's guide](https://github.com/pydemull/activAnalyzer/blob/master/inst/guide/user_guide_en.pdf) for details about how the app works.

## Usage

There are three different ways to use the activAnalyzer app:

* [On the web via a shinyapps.io plateform](https://pydemull.shinyapps.io/activAnalyzer/) (stable version). For information, as indicated by [RStudio](https://www.shinyapps.io/), "*shinyapps.io is secure-by-design. Each Shiny application runs in its own protected environment and access is always SSL encrypted*". Importantly, the app is hosted using a free account that allows to run apps for 25 hours per month. Thus, the availability of the app on the web is very dependent on the number of users as well as the time spent by each user on the app. That's why the second option available to use the app (see below) may be more appropriate (for Windows users only).
* [Locally on PC via a standalone desktop app](https://sourceforge.net/projects/activanalyzer)  that is downloadable from the SourceForge website (stable version, for Windows machines only). The standalone app has been developped using the framework *DesktopDeployR* kindly made available by [W. Lee Pang](https://github.com/wleepang). Explanations related to this framework can be retrieved from [a dedicated GitHub repository](https://github.com/wleepang/DesktopDeployR). Once the app is installed on your PC, you will have to double-click on the desktop app icon (if you have chosen this option during the installation process), which will run the R-portable version embedded in the app and then will launch the app in your default web browser with 127.0.0.1 as the value for the host parameter. This means that only your current machine will can access the app. You will can open only one session at a time. Google Chrome and Microsoft Edge browsers allow the app to work as expected but Mozilla Firefox does not seem to allow reseting all the inputs when required.
* Locally on your machine via [R software](https://cran.rstudio.com/), the [RStudio environment](https://www.rstudio.com/), and the [activAnalyzer package](https://github.com/pydemull/activAnalyzer) installable from GitHub (development version). To be able to generate the .pdf reports, you will have to install the [TinyTeX distribution](https://yihui.org/tinytex/). In short, after installing R and RStudio, you can run the following command lines in the RStudio console:

``` {r in, eval=FALSE}
# Code for installing the activAnalyzer package
install.packages("devtools")
devtools::install_github("pydemull/activAnalyzer")

# Code for installing the TinyTex distribution 
tinytex::install_tinytex()
```

## Example

To launch the app using R:

```{r install, eval=FALSE}
library(activAnalyzer)
activAnalyzer::run_app()
```


```{r, include=FALSE, eval=FALSE}
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date:
devtools::build_readme()

You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.
```

## Code of Conduct

Please note that the activAnalyzer project is released with a [Contributor Code of Conduct](https://pydemull.github.io/activAnalyzer/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
