---
title: "activAnalyzer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{activAnalyzer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The activAnalyzer package was primarily built for working through a shiny app. The procedure for using the app is explained in the related [user's guide](https://github.com/pydemull/activAnalyzer/blob/master/inst/guide/user_guide_en.pdf). The functions used in this app can also be used to analyze data outside the app, as shown below.

## Loading packages
```{r setup}
library(activAnalyzer)
library(magrittr)
library(ggplot2)
```

## Getting file
```{r}
file <- system.file("extdata", "acc.agd", package = "activAnalyzer")
```

## Preparing dataset
```{r, warning=FALSE, message=FALSE}
mydata <- prepare_dataset(data = file, epoch_len_out = 60, col_time_stamp = "timestamp")
```

## Getting nonwear/wear time marks
```{r, message = FALSE, fig.width = 7, fig.height = 5, fig.align='center'}
mydata_with_wear_marks <- 
  mydata %>%
  mark_wear_time(frame = 90, allowanceFrame = 2, streamFrame = 30)

plot_data(data = mydata_with_wear_marks, metric = "vm")
```

## Getting physical activity intensity marks
```{r, message = FALSE, fig.width = 7, fig.height = 5, fig.align='center'}
mydata_with_intensity_marks <- 
  mark_intensity(data = mydata_with_wear_marks, 
    equation = "Sasaki et al. (2011) [Adults]", 
    age = 32, 
    weight = 67, 
    sex = "male")

plot_data_with_intensity(mydata_with_intensity_marks)
```

## Getting results by day
```{r, message = FALSE}
results_by_day <-
  mydata_with_intensity_marks %>%
  recap_by_day(age = 32, weight = 67, sex = "male")

results_by_day %>%  
  reactable::reactable(  
           striped = TRUE,
           list(total_counts_axis1 = reactable::colDef(minWidth = 150),
                total_counts_vm = reactable::colDef(minWidth = 150),
                minutes_SED = reactable::colDef(minWidth = 120),
                minutes_LPA = reactable::colDef(minWidth = 120),
                minutes_MPA = reactable::colDef(minWidth = 120),
                minutes_VPA = reactable::colDef(minWidth = 120),
                minutes_MVPA = reactable::colDef(minWidth = 125),
                percent_SED = reactable::colDef(minWidth = 120),
                percent_LPA = reactable::colDef(minWidth = 120),
                percent_MPA = reactable::colDef(minWidth = 120),
                percent_VPA = reactable::colDef(minWidth = 120),
                percent_MVPA = reactable::colDef(minWidth = 125),
                ratio_mvpa_sed = reactable::colDef(minWidth = 130),
                total_kcal_wear_time = reactable::colDef(minWidth = 165),
                mets_hours_mvpa = reactable::colDef(minWidth = 160))
           )
```

## Getting results averaged over valid days
```{r}
averaged_results <-
  results_by_day %>%
  average_results(minimum_wear_time = 10)

averaged_results %>% 
    reactable::reactable(
    list(valid_days = reactable::colDef(minWidth = 90),
         wear_time = reactable::colDef(minWidth = 90),
         total_counts_axis1 = reactable::colDef(minWidth = 150),
         total_counts_vm = reactable::colDef(minWidth = 150),
         minutes_SED = reactable::colDef(minWidth = 120),
         minutes_LPA = reactable::colDef(minWidth = 120),
         minutes_MPA = reactable::colDef(minWidth = 120),
         minutes_VPA = reactable::colDef(minWidth = 120),
         minutes_MVPA = reactable::colDef(minWidth = 125),
         percent_SED = reactable::colDef(minWidth = 120),
         percent_LPA = reactable::colDef(minWidth = 120),
         percent_MPA = reactable::colDef(minWidth = 120),
         percent_VPA = reactable::colDef(minWidth = 120),
         percent_MVPA = reactable::colDef(minWidth = 125),
         ratio_mvpa_sed = reactable::colDef(minWidth = 130),
         total_kcal_wear_time = reactable::colDef(minWidth = 165),
         mets_hours_mvpa = reactable::colDef(minWidth = 160)),
    striped = TRUE
  )
```




